\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=1.2cm,bottom=1.5cm,left=1.5cm,right=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{multicol}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}{\bfseries\scshape\large}{}{0em}{}

\begin{document}

% Header
{\LARGE \textbf{Kumar Shantanu}}\\
\href{mailto:kumarshantanu0023@gmail.com}{kumarshantanu0023@gmail.com} \hfill 
\href{https://www.linkedin.com/in/kumar-shantanu23/}{linkedin.com/in/kumar-shantanu23} \hfill 
\href{https://github.com/KumarShantanu23}{GitHub: KumarShantanu23}
\vspace{-1em}

\rule{\textwidth}{0.4pt}

% Summary
\noindent BTech CSE student skilled in software development, AI, and cloud platforms (AWS, GCP). Proficient in React, Node.js, and solving real-world problems. Passionate about scalable systems and data privacy.

% Skills
\vspace{-0.2em}
\section*{Skills}
\begin{tabular}{p{0.5\textwidth} p{0.5\textwidth}}
\begin{itemize}[leftmargin=1em, itemsep=0.1em]
    \item C, C++, Java, Python, HTML, CSS, JavaScript
    \item Node.js, Express, React, Tailwind CSS, Figma
    \item AWS, GCP
\end{itemize}
&
\begin{itemize}[leftmargin=5em, itemsep=0.1em]
    \item English (Proficient)
    \item Hindi (Native)
\end{itemize}
\end{tabular}



% Projects
\vspace{-0.5em}
\section*{Projects}
\textbf{Machine Learning based intrusion detection system} \hfill 
\vspace{-1em}
\textit{Scikit-learn, Pandas, NumPy, Matplotlib, Seaborn} \\
\begin{itemize}[leftmargin=1em,label=, itemsep=0.3em]
    \item A Machine Learning-based Intrusion Detection System designed using the CIC-IDS2017 dataset to detect various types of cyberattacks. The project evaluates multiple ML algorithms to determine the most effective model for real-time threat detection.
\end{itemize}

% Experience
\vspace{-0.4em}
\section*{Experience}
\textbf{\href{https://aictecert.eduskillsfoundation.org/pages/home/verify.php?cert=900f6c35bef91fd0d43463e96e0400a8}{Cloud Virtual Intern – AWS Academy (via Eduskills)}} \hfill \textit{Oct 2024 – Dec 2024} \\
Completed the AWS Academy Cloud Foundations and Architecting modules. Gained hands-on experience in designing and simulating cloud architectures using core AWS services.

\vspace{0.3em}
\textbf{\href{https://aictecert.eduskillsfoundation.org/pages/home/verify.php?cert=adfeefde2b3ca41257418d77ba4514e0}{AI-ML Virtual Intern – Google (via Eduskills)}} \hfill \textit{Jan 2025 – Mar 2025} \\
Worked on machine learning fundamentals, model building, and responsible AI. Explored real-world use cases and built small ML applications using Google Cloud tools.

% Strengths
\vspace{-0.4em}
\section*{Strengths}
\begin{tabularx}{\textwidth}{XXX}
\textbf{\textcolor{blue}{Problem Solving}} & \textbf{\textcolor{blue}{Technical Proficiency}} & \textbf{\textcolor{blue}{Quick Learner}} \\
Improved team workflow by 20\% by addressing bottlenecks. & Versed in full-stack development and cloud infrastructure. & Adaptable to new technologies and eager to expand technical knowledge.
\end{tabularx}
\normalsize

% Education & Achievements in two columns
\vspace{-0.5em}
\section*{Education \& Achievements}
\begin{multicols}{2}
\textbf{B.Tech CSE} \\
KIIT, Bhubaneswar \\
2022 – 2026

\vspace{0.3em}
\textbf{Senior Secondary (XII)} \\
St. Joseph’s High School, Patna

\vspace{0.3em}
\textbf{Secondary (X)} \\
St. Joseph’s High School, Patna

\columnbreak

\begin{itemize}[leftmargin=1em, itemsep=0.3em]
    \item {Represented School and College in National Basketball Events}
    \item \href{https://www.credly.com/badges/4e904b52-e5d0-4a34-8ba2-a0fd863d9b9b/print}{AWS Cloud Foundations}
    \item \href{https://www.credly.com/badges/7ae8b6ab-d30e-4a75-8c1b-9c3b4673bb30/print}{AWS Cloud Architecting}
\end{itemize}
\end{multicols}
\end{document}
